ms2

### 2017-05-04 ms2/ms2.Rmd
fixed merging

**swo**: filter the NAs in the abg earlier

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      pdf.options(useDingbats=FALSE),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
import::from(pander, pander)
import::from(broom, tidy)
```

@@

# Keep only bug/drug combinations that are in at least 75 HRRs
min_n_states = 35
good_combos = possible_bug_drug %>%
  left_join(abg, by=c('bug', 'drug_group')) %>%
  select(bug, drug_group, state) %>%
  distinct %>%
  count(bug, drug_group) %>% rename(n_places=n) %>%
  filter(n_places >= min_n_states)

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      pdf.options(useDingbats=FALSE),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE)
import::from(broom, tidy)
```

@@

# Keep only bug/drug combinations that are in at least 75 HRRs
min_n_states = 35
good_combos = semi_join(abg, possible_bug_drug, by=c('bug', 'drug_group')) %>%
  select(bug, drug_group, state) %>%
  distinct %>%
  count(bug, drug_group) %>% rename(n_places=n) %>%
  filter(n_places >= min_n_states)
